Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-05-05 fib2.tex
correct spelling of "acknowledgments"
minor edits, added some refs.

Topologically ordered quantum systems in two dimensions offer tremendous promise for long-term storage and processing of quantum 
information~\cite{Dennis2002} \cggb{a relevant review reference?}. The topological features of such systems are insensitive to local perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations displaying anyonic statistics~\cite{Wilczek1990}. These anyons can in general be used as quantum memories or to perform universal topological quantum computation~\cite{Kitaev2003, Freedman2002, Nayak2008}.

@@

Almost all of the sizable research effort on active quantum error correction for topological 
systems has focused on the case of abelian anyons~\cite{Terhal2014} \cggb{revise citations here: poulin decoding stuff, what else?}. These systems are 
well suited to studying quantum error correction because the dynamics of excitations in 
abelian anyon models (at the RG fixed point) can be simulated numerically very efficiently, allowing lattice 
simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. Standard algorithms to efficiently simulate these systems rely on the abelian nature of these particles, and in particular the fact that abelian anyons cannot be used for quantum computation.

@@

We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
microscopic details of the system. 
\dude{Another way of saying this is that we are doing a tqft simulation.}
This is consistent with the principles of topologically 
ordered systems and anyonic physics, where the key universal features describing the 
anyon model correspond to large length-scale physics, while the microscopic physics plays 
a less important (and non-universal) role. As such, we model the system simply as a 
periodic $L\times L$ square lattice $\Lambda$ of sites with upon which sets of anyons can 
reside. Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
locally on edges of $\Lambda$. For more details of an analogous model, see~\cite{Brell2013}.

@@

%------------------------------------------------------------------------------------------------------------%
\acknowledgements

>>>>

Topologically ordered quantum systems in two dimensions offer tremendous promise for 
long-term storage and processing of quantum information~\cite{Brown2015, Terhal2015}. 
The topological features of such systems are insensitive to local 
perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations 
displaying anyonic statistics~\cite{Wilczek1990}. These anyons can in general be used as 
quantum memories~\cite{Kitaev2003, Dennis2002} or to perform universal topological 
quantum computation~\cite{Freedman2002, Nayak2008}.

@@

Almost all of the sizable research effort on active quantum error correction for topological 
systems has focused on the case of abelian anyons~\cite{Terhal2015} \cggb{revise citations here: poulin decoding stuff~\cite{Duclos-Cianci2010, Duclos-Cianci2010a, Duclos-Cianci2013}, what else?} \stf{Dan Browne's recent work, Bravyi's recent work, Austin Fowler? Do we really want to cite everyone that's ever decoded the toric code?}. These systems are 
well suited to studying quantum error correction because the dynamics of excitations in 
abelian anyon models (at the RG fixed point) can be simulated numerically very efficiently, allowing lattice 
simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. Standard algorithms to efficiently simulate these systems rely on the abelian nature of these particles, and in particular the fact that abelian anyons cannot be used for quantum computation.

@@

We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
microscopic details of the system. 
\dude{Another way of saying this is that we are doing a tqft simulation.}
This is consistent with the principles of topologically 
ordered systems and anyonic physics, where the key universal features describing the 
anyon model correspond to large length-scale physics, while the microscopic physics plays 
a less important (and non-universal) role. As such, we model the system simply as a 
periodic $L\times L$ square lattice $\Lambda$ of sites upon which sets of anyons can 
reside. Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
locally on edges of $\Lambda$. For more details of an analogous model, see~\cite{Brell2013}.

@@

%------------------------------------------------------------------------------------------------------------%
\acknowledgments
